### 2015-12-29 notebook/2015-12-28-eml-explore.Rmd
a few improvements

```{r}
library("EML")
library("purrr")
library("dplyr")
```

@@

stuff[[1]]
```

@@

```{r}
slotNames(stuff[1])

@@

```{r}
purrr::map_df(stuff, function(x) data.frame(column.name = x@attributeName, definition = x@attributeDefinition))

# Or identically with dplyr alone:
#dplyr::bind_rows(lapply(stuff, function(x) data.frame(column.name = x@attributeName, definition = x@attributeDefinition)))

do.call(rbind, lapply(stuff, function(x) data.frame(column.name = x@attributeName, definition = x@attributeDefinition)))

This creates a `data.frame` with two columns: the name of every column in Table 4, and a description of what each of those 29 columns contains.  Similarly we can create a `data.frame` that summarizes all of the tables in the dataset:

>>>>

```{r message=FALSE}
library("EML")
library("purrr")
library("dplyr")
knitr::opts_chunk$set(comment=NA, warning=FALSE)

# Wide tables, since we can scroll left/right
options("dplyr.width" = Inf, "width" = 1000)
```

@@

stuff[1]
```

@@

```{r}
slotNames(stuff[[1]])

@@

```{r}
purrr::map_df(stuff, function(x) data.frame(column.name = x@attributeName, definition = x@attributeDefinition))
```

(Or if you don't like `purrr` and the hadley magic, the same thing with base R:)

```{r eval=FALSE}
do.call(rbind, lapply(stuff, function(x) data.frame(column.name = x@attributeName, definition = x@attributeDefinition)))
```

Either way, this creates a `data.frame` with two columns: the name of every column in Table 4, and a description of what each of those 29 columns contains.  Similarly we can create a `data.frame` that summarizes all of the tables in the dataset:
